How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-09 tse-paper/content.tex
Xupdated graphics, adding anecdotal results to literature study

\begin{figure}[tbhp]
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/lit-sur/log_producer_long-cropped.pdf}
		\caption{Frequency of supported log producer.}
		\label{fig:litsur:log_producer}
\end{figure}

\subsubsection{Retrieved Information}
The information that was targeted is presented in
\Cref{fig:litsur:info_target} varied from article to article.
Most prominent was the search for errors (39\%) that occured within
the build process, followed by extracting the executed or the failing
tests (both 11\%).

In most cases (51\%), a chunk was retrieved from the log, whereas 36\%
of the articles classified the articles into categories.
Other types of processing (e.g.
counting lines, summarization) were only
done in one case each.

@@

The most mentioned method (34\%) was using a parser, where we also
included
rather unprecise statements like ``we parse the build logs''.
25\% of the articles described the use of regular expressions and 20\%
inspected the logs manually.
Another 8\% employed machine learning techniques such as natural language
processing or information retrieval techniques.

@@

Seo et al.~\cite{seo2014programmers}
They based their analyses on sets of
build logs collected from industry partners.
They develop a custom
parser to classify error messages reported by Java and C++ builds.

Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open
source Java projects

Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects
in Java to industrial ones.
Their data stems from analyzing
build logs from \emph{TravisTorrent}~\cite{beller2017travistorrent}
with regular expressions.

Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build
breakage data.
They classify build failures from \emph{TravisTorrent}
Their analysis starts with manual
categorization of build logs.
They select keywords and strings that
identify their targeted categories and code a script to automatically
classify logs based on these keywords.
% TODO note which technique words we assined here

Vassallo et
al.~\cite{vassallo2018un-break}
They parse
Maven~\cite{maven2019website} build logs into a structured
representation and create hint generators.
For example, one of the hint generators queries stack overflow for
discussions related to why the build failed.
The chunk retrieval techniques we compare in this article can be used
to fill similar structured representations with information from build
logs.
As they simplify the construction of parsers they would enable
developers and researchers to cover a wider array of build tools,
which is the main influence factor on the structure of a build log.

Amar et al.~\cite{amar2019mining} compare different approaches to
reduce the portions of a log that a developer has to inspect.
Their
techniques remove lines that appear both in logs from passing and
failing builds and use a modified \emph{Term Frequency Inverse
Document Frequency} (TF-IDF) weighting to identify term vectors likely
to occur with failures.
Their diff technique can be interpreted as a
chunk retrieval technique, where the targeted information is defined
by the past failures used as basis for the weighted term vectors.

@@

31\% of the surveyed articles claimed to have published their data to
enable further research.

@@

% TODO Caro: redo
\begin{figure*}[tb]
	\centering
	\includegraphics[width=\textwidth, trim={0.5cm 1.3cm 0.2cm 0.3cm},
  clip]{img/study.pdf}
	\caption{Design of our technique comparison study.}
	\label{fig:study}
\end{figure*}

@@

\subsection{Keyword Search (KWS)}
\label{sec:r:kws}
\begin{figure*}
\centering
    \textbf{Keyword Search (KWS)}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
		\caption{training set size.\\ \,}
    % top-aligning captions
		\label{fig:recall-precision-examplecount-KWS}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
		\caption{structural category count
		in training and test sets.}
		\label{fig:recall-precision-categorycount-KWS}
\end{subfigure}
\caption{Precision, recall and F$_{1}$-score of chunk retrieval with
Keyword Search (KWS) compared by \ldots}
\end{figure*}

@@

\begin{figure*}
\centering
    \textbf{PBE, CTS, KWS, and RLR}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
				\includegraphics[width=\columnwidth,
				clip]{img/big-study/recall-precision-singlecategory-all.pdf}
		\caption{Training and test examples in \emph{one}
		structural category.\\ \,}
    % top-aligning captions
		\label{fig:recall-precision-singlecategory-all}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
				\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-multicategory-all.pdf}
		\caption{Training and test examples in $>1$ structural
		category.}
		\label{fig:recall-precision-multicategory-all}
\end{subfigure}
\caption{Precision, recall and F$_{1}$-score of all
techniques compared, split by structural category count.}
\end{figure*}

@@

Seo et al.~\cite{seo2014programmers}
They based their analyses on sets of
build logs collected from industry partners.
They develop a custom
parser to classify error messages reported by Java and C++ builds.

Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open
source Java projects

Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects
in Java to industrial ones.
Their data stems from analyzing
build logs from \emph{TravisTorrent}~\cite{beller2017travistorrent}
with regular expressions.

Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build
breakage data.
They classify build failures from \emph{TravisTorrent}
Their analysis starts with manual
categorization of build logs.
They select keywords and strings that
identify their targeted categories and code a script to automatically
classify logs based on these keywords.
% TODO note which technique words we assined here

Vassallo et
al.~\cite{vassallo2018un-break}
They parse
Maven~\cite{maven2019website} build logs into a structured
representation and create hint generators.
For example, one of the hint generators queries stack overflow for
discussions related to why the build failed.
The chunk retrieval techniques we compare in this article can be used
to fill similar structured representations with information from build
logs.
As they simplify the construction of parsers they would enable
developers and researchers to cover a wider array of build tools,
which is the main influence factor on the structure of a build log.

Amar et al.~\cite{amar2019mining} compare different approaches to
reduce the portions of a log that a developer has to inspect.
Their
techniques remove lines that appear both in logs from passing and
failing builds and use a modified \emph{Term Frequency Inverse
Document Frequency} (TF-IDF) weighting to identify term vectors likely
to occur with failures.
Their diff technique can be interpreted as a
chunk retrieval technique, where the targeted information is defined
by the past failures used as basis for the weighted term vectors.

>>>>

\begin{figure}[tbhp]
		\centering
		\includegraphics[width=\columnwidth, trim={1.1cm 0.4cm
		1.5cm 0.5cm},
		clip]{img/lit-sur/log_producer_annotated.pdf}
		\caption{Frequency of supported log producer.}
		\label{fig:litsur:log_producer}
\end{figure}

\subsubsection{Retrieved Information}
The information that was targeted is presented in
\Cref{fig:litsur:info_target} varied from article to article.
Most prominent was the search for errors (39\%) that occured within
the build process, followed by extracting the executed or the failing
tests (both 11\%).
There were also numerous cases which targeted more specialized
information, such as the environments used during the
build~\cite{zolfagharinia2017not}, packages
installed~\cite{selberg2012use} or hints to source files which are
related to build failures~\cite{ren2018automated}.

In most cases (51\%), a chunk was retrieved from the log.
Cemencic and Couturier~\cite{clemencic2014new}, for example,
scan build logs for compilation errors, while Zhang et
al.~\cite{zhang2016android} retrieve the duration of
tasks within the build.

The articles classified the build logs into categories in 36\% of
the cases.
Didrik Lindqvist~\cite{lindqvist2019detection} used build logs to
distuinguish failures caused by
developers from those caused by infrastructure, while
Kavaler et al.~\cite{kavaler2019tool} idenfity projects that use
automated static analysis tools.
Other types of information (e.g.
counting lines, summarization) were only retrieved
in one case each.

@@

The most mentioned method (34\%) was using a parser, where we also
included
rather unprecise statements like ``we parse the build logs''.
25\% of the articles described the use of regular expressions and 20\%
inspected the logs manually.
Another 8\% employed machine learning techniques such as natural language
processing or information retrieval techniques.
For example,
Seo et al.~\cite{seo2014programmers} developed a custom
parser to classify error messages, while Vassallo et
al.~\cite{vassallo2017a-tale} analyzed build logs with regular
expressions.
Ghaleb et al.~\cite{ghaleb2019studying} used a compound approach.
They start with manual categorization of the build logs and select
search strings that identify their targeted categories.
Based on the search strings they create a script which automatically
classifies the remaining logs.
%TODO: they are not actually in our survey, the talk about 'test logs'
Amar et al.~\cite{amar2019mining} compare different approaches to
reduce the number of lines to be inspected by the developer.
Their best performing technique creates a diff between the logs from a
successful and a failed build and ranks the remaining lines using
Information Retrieval (IR) techniques.

@@

% Seo et al.~\cite{seo2014programmers}
% They based their analyses on sets of
% build logs collected from industry partners.
% They	reported by Java and C++ builds.

% Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open
% source Java projects

% Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects
% in Java to industrial ones.
% Their data stems from analyzing
% build logs from \emph{TravisTorrent}~\cite{beller2017travistorrent}
% with regular expressions.

% Vassallo et
% al.~\cite{vassallo2018un-break}
% They parse
% Maven~\cite{maven2019website} build logs into a structured
% representation and create hint generators.
% For example, one of the hint generators queries stack overflow for
% discussions related to why the build failed.

@@

31\% of the surveyed articles claimed to have published their data to
enable further research.
However we found no clear reuse of build log data sets with the
exception of TravisTorrent~\cite{beller2017travistorrent}, which was
analyzed by Vassallo et al.~\cite{vassallo2017a-tale},
Ghaleb et al.~\cite{ghaleb2019studying} and several other studies.

@@

% TODO Caro: redo
\begin{figure*}[tb]
	\centering
	\includegraphics[width=\textwidth, trim={1.6cm 1.6cm 0.2cm 5.6cm},
  clip]{img/study.pdf}
	\caption{Design of our technique comparison study.}
	\label{fig:study}
\end{figure*}

@@

\subsection{Keyword Search (KWS)}
\label{sec:r:kws}
\begin{figure*}
\centering
    \textbf{Keyword Search (KWS)}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
		\caption{training set size.}
		\label{fig:recall-precision-examplecount-KWS}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
		\caption{structural category count
		in training and test sets.}
		\label{fig:recall-precision-categorycount-KWS}
\end{subfigure}
\caption{Precision, recall and F$_{1}$-score of chunk retrieval with
Keyword Search (KWS) compared by \ldots}
\end{figure*}

@@

\begin{figure*}
\centering
    \textbf{PBE, CTS, KWS, and RLR}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
				\includegraphics[width=\columnwidth,
				clip]{img/big-study/recall-precision-singlecategory-all.pdf}
		\caption{Training and test examples in \emph{one}
		structural category.}
		\label{fig:recall-precision-singlecategory-all}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
				\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-multicategory-all.pdf}
		\caption{Training and test examples in $>1$ structural
		category.}
		\label{fig:recall-precision-multicategory-all}
\end{subfigure}
\caption{Precision, recall and F$_{1}$-score of all
techniques compared, split by structural category count.}
\end{figure*}

@@
